Scalar_M1

### 2015-05-28 models/Model_Playspace.Rmd
Committing preliminary integration with Yelp data

```{r}
priors = read.csv("models/prior.csv")
# Possible transformations --->
priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
#priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
#priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))
speaker = read.csv("models/speaker.csv")
#speaker.alt = read.csv("models/e5a.csv")
listener = read.csv("models/listener.csv")
```

@@

@@

  if (usenone) {
    mat$none <- c(.9, .1, 0, 0, 0)
    mat$neg_valence <- c(.2, .5, .2, .1, 0)
  }

@@

```{r}
# Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=20)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = TRUE, usenone = TRUE))

  mean((md$pred - md$listener.p)^2)
  #cor(md$pred, md$listener.p)
})
qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
best.alpha = which(fit == min(fit))
best.alpha

# RUN MODEL
md <- data %>%
  do(run.rsa(., alpha = best.alpha, useprior = TRUE, usenone = TRUE))
```

@@

Speaker informativity measures
```{r}
# Scalar judgment scores by rating
qplot(x = stars, y = speaker.judgment, col = degree, ymax = 5,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = speaker, main= "Scalar + Rating compabililty") + 
  geom_linerange(aes(ymin = speaker.judgment - speaker.cil, 
                     ymax = speaker.judgment + speaker.cih)) + 
  facet_wrap(~scale)

>>>>

```{r}
priors = read.csv("models/prior.csv")

# Yelp priors
priors$prior.p = c(0.09020902, 0.10561056, 0.16281628, 0.30463046, 0.33673367)
# Possible transformations --->
priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
#priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
#priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))
speaker = read.csv("models/speaker.csv")
#speaker = read.csv("models/e5a.csv")
speaker = read.csv("models/yelp1.csv")
listener = read.csv("models/listener.csv")
```

@@

# speaker.prob = function(rating, degree, m, alpha) {
#   p = m[rating, degree] / sum(m[rating, ])
#   
#   return(p)
# }

@@

  if (usenone) {
    mat$none <- c(.9, .1, 0, 0, 0)
    mat$bad <- c(.5, .9, .4, .1, 0)
  }

@@

```{r}
# Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=20)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))

  #mean((md$pred - md$listener.p)^2)
  cor(md$pred, md$listener.p)
})
qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
best.alpha = which(fit == max(fit))
best.alpha

# RUN MODEL
md <- data %>%
  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
```

@@

Speaker informativity measures
```{r}
# Scalar judgment scores by rating
qplot(x = stars, y = speaker.judgment, col = degree, ymax = 5,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = speaker, main= "Scalar + Rating compabililty") + 
  #geom_linerange(aes(ymin = speaker.judgment - speaker.cil, 
  #                   ymax = speaker.judgment + speaker.cih)) + 
  facet_wrap(~scale)
